Need a good title. Submit to Methods of Ecology and Evolution or Evolutionary Biology

### 2018-03-07 main.tex
finish up in the am

Incorportating phylogenetic links between species and combine evolutionary changes with statistical processes advances the development of phylogenetic comparative methods.
The most widely used statistical process in phylogenetic comparative analysis to model evolutionary process is the pure random drift process, Brownian motion \citep{felsenstein1973maximum}. 
Although the Brownian motion is an over-simplified model of evolution, many of the existing phylogenetic comparative methods are built upon.
For example, phylogenetic regression via independent contrasts \citep{felsenstein1985phylogenies}, phylogenetic generalized least squares \citep{grafen1989phylogenetic}, Pagel's $\lambda$ \citep{pagel1999inferring}, Blomberg's $K$ \citep{blomgerg2003} are methods developed in the last couple of decades and have provided important insights in this field. 
Nevertheless, there are also a handful of selection beyond the pure random drift (BM) process where they probe specific aspects of the evolutionary process (i.e. Ornstein-Uhlenbeck (OU) process which accounts for both selection and drift processes, Pagel's $\delta$ and $\kappa$ transformations where it explores variation of evolutionary rates and speciational changes through time respectively).

@@

@@

In this paper, we propose an alternative, yet straightforward but little-used method of constructing phylogenetic correlations directly from phylogenetic tree by summing the evolutionary changes that occurred on all of the branches in the phylogeny in its past.

\ml{flexabilitiy: multiple obs per species and multiple levels of phylogenetic signal}
We apply relatively simple phylogenetic comparative approaches to data from simulated phylogenies that incorportate various complexity of phylogenetic signals in the model. 
We compare model approaches and explore various complex modelling strategies in the mixed model framework and a flexible platform for researches to explore biologically interesting questions.

@@

We generated test data based on the simple mixed model formulation \ml{ref equation (3-5)} with a single response variable $Y$ and a single predictor continuous variable $X$ from $n$ (20, 100, and 500) species, and $m$ (1 and 20) sites. 
To account for multiple levels of phylogenetic signal, we assume phylogenetic signal in the intercept $b_0$, and slope $b_1$.
We further assume that random slope and intercept are correlated. 
For models with multiple sites, we also assume for species and site interactions random effects, an equilvalent version of nested random effects or phylogenetic attraction described in \cite{helmus2007separating} with the main random effects.

Many platforms 
- single observations per species (IC and pgls)
- single observation per species per site (pez)
- lme4 does everything

@@

The simulation models is based on glmm framework described in \ml{eq labels 3-5}.   
To construct the simulation model, let $n$ be the number of species distributed among $m$ sites.
Let $Y$ be the $mn \times 1$ vectors of response trait.  
We generate test data using three different $n$ (20, 100, 500) and two different $m$ (1, 20) using a simple glmm framework that varies in complexity in random effect described in \ml{Table 1, macro this with labels}. 
We also extend the multiple site models described in \ml{Table 1} with species by site interaction random effects. 
All simulations and fits were performed with R.

\subsection{Model Fitting}

@@

\section{Discussion}
\section{Conclusion}
\newpage
\section{translation}

>>>>

Incorportating phylogenetic links between species and combine evolutionary changes with statistical processes advances the development of phylogenetic comparative methods.
The most widely used statistical process in phylogenetic comparative analysis to model evolutionary process is the pure random drift process, Brownian motion \citep{felsenstein1973maximum}. 
Although the Brownian motion is an over-simplified model of evolution, many of the existing phylogenetic comparative methods are built upon.
For example, phylogenetically independent contrasts (PICs) \citep{felsenstein1985phylogenies}, phylogenetic generalized least squares (PGLS) \citep{grafen1989phylogenetic}, Pagel's $\lambda$ \citep{pagel1999inferring}, and Blomberg's $K$ \citep{blomberg2003testing} are methods developed in the last couple of decades and have provided important insights in this field. 
Nevertheless, there are also a handful of selection beyond the pure random drift (BM) process where they probe specific aspects of the evolutionary process (i.e. Ornstein-Uhlenbeck (OU) process which accounts for both selection and drift processes, Pagel's $\delta$ and $\kappa$ transformations where it explores variation of evolutionary rates and speciational changes through time respectively).

@@

\ml{write a paragraph on pglmm? Flexbility paragraph and say PIC/GLS assumes the tpoplogy and branch lengths are error free, Pagel's lambda and Blomberg's K accounts for additional tip variations of the phylogeny, to account for additional variation such as measurement error and such, people turn to Bayesian mixed models \cite{de2012bayesian, hadfield2010general}}

@@

In this paper, we propose an alternative, yet straightforward but little-used method of constructing phylogenetic correlations directly from phylogenetic tree by summing the evolutionary changes that occurred on all of the branches in the phylogeny in its past.
\ml{flexabilitiy: multiple obs per species and multiple levels of phylogenetic signal}
We apply relatively simple phylogenetic comparative approaches to data from simulated phylogenies that incorportate various complexity of phylogenetic signals in the model and measurement errors. 
We compare model approaches and explore various complex modelling strategies in the mixed model framework and a flexible platform for researches to explore biologically interesting questions.

@@

We generated test data based on the simple mixed model formulation \ml{ref equation (3-5)} with a single response variable $Y$ and a single predictor continuous variable $X$ from $n$ (20, 100, and 500) species, and $m$ (1 and 20) sites. 
To account for multiple levels of phylogenetic signal, we assume phylogenetic signal in the intercept $b_0$, and slope $b_1$.
We further assume that random slope and intercept are correlated. 
For models with multiple sites, we also assume for species and site interactions random effects, an equilvalent version of nested random effects or phylogenetic attraction described in \cite{helmus2007separating} with the main random effects.
Table \ml{ref something} provides the statistially equilvalent fitting capabilities of common/existing phylogenetic methods.

@@

@@

\begin{center}
\begin{figure}[h]
\includegraphics[scale=0.8,page=1]{./git_push/ssplot.pdf}
\label{ssplot}
\end{figure}
\end{center}

The full model (which matches the simulations model that incorportates phylogenetic signal on the intercept, slope and correlation) provides good estimates of the different levels of the phylogenetic variation signal (Figure 1 and 2).

In general, as the number of species (or phylogeny) increases, all phylogenetic signal estimates are more robust for all models (including models without random slope and correlation) except PGLS in the single site simulations. 
It is unclear how different levels of phylogenetic signal is being confounded under the error free (without tip variation) assumption for the PGLS models.
The estimated phylogenic signal estimates appear to be increasing as the number of species increase.

\begin{center}
\begin{figure}[h]
\includegraphics[scale=0.8,page=1]{./csplot.pdf}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
\includegraphics[scale=0.8,page=2]{./csplot.pdf}
\end{figure}
\end{center}

% \begin{center}
% \begin{figure}[h]
% \includegraphics[scale=1]{./ssplot.pdf}
% \end{figure}
% \end{center}

\newpage

\section{Discussion}

large datasets
limitations (unbalance datasets)
this trick works in bayesian/mcmc framework

\newpage

\section{Conclusion}

\newpage

\section{translation}
